### 2013-10-30 index.Rmd
The structure of the document is set

% Attributions for Poverty in Post-Socialist Countries
% Markus Kainu & Mikko Niemelä
% Jan 2013

<link href="http://markuskainu.fi/material/css/article_wide.css" rel="stylesheet" type="text/css" title="compact"></link>
<link href='http://fonts.googleapis.com/css?family=Alegreya+SC|Dosis:400,200' rel='stylesheet' type='text/css'>

@@

cd ~/workspace/lits/attrib/attrib_year2013
lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/
```

******

<center>
<table>
<tr>
<td>[Etusivu](index.html)</td>
<td>[Descriptive analysis](code/descriptive_analysis.html)</td>
<td>[Output tables in html](code/multilevel_models.html)</td>
<td>[Output tables in pdf](code/multilevel_models.pdf)</td>
<td>[Article in pdf](article2013.pdf)</td>
<td>[Article in html](article2013.html)</td>
<td>[Presentation slides](slides/slides_attrib.html)</td>
</tr>
</table>
</center>

*******

# Etusivu

>>>>

% Attributions for Poverty in Post-Socialist Countries
% Markus Kainu & Mikko Niemelä
% Nov 2013

<link href="http://markuskainu.fi/material/css/rmarkdown.css" rel="stylesheet" type="text/css" title="compact"></link> <link href='http://fonts.googleapis.com/css?family=Oswald' rel='stylesheet' type='text/css'>

@@

cd ~/workspace/lits/attrib/attrib_year2013/figures
lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/
```

# Introduction

# Data Analysis

## Cleaning the data & missing data

html-ouput                                                    source code
-------------------------------------------------------       -----------------------------
[loading and cleaning](code/descriptive_analysis.html)        [source](code/descriptive_analysis.Rmd)
[missing data & diagnostics](code/descriptive_analysis.html)  [source](code/descriptive_analysis.Rmd)

## Descriptive analysis

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Descriptive analysis](code/descriptive_analysis.html)    [source](code/descriptive_analysis.Rmd)

## Modelling the data

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Output tables in html](code/multilevel_models.html)      [source](code/multilevel_models.Rmd)
[Output tables in pdf](code/multilevel_models.pdf)        [source](code/multilevel_models.Rmd)

# Paper

html-output                                               source code
-------------------------------------------------------   -----------------------------
[Article in html](article2013.html)                       [Article in pdf](article2013.pdf)

# Presentation slides

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Presentation slides](slides/slides_attrib.html)          [source](code/multilevel_models.Rmd)
